---
title: "Assignment 1"
output: pdf_document
date: "2024-02-11"
---

```{r setup, include=FALSE}
netflix <- read.csv("C:/Users/Dhvanil/Desktop/Courses/4066 Intro to Analytical System/netflix1.csv")
library(DescTools)
```

Question 1 - Print the structure of your dataset.


```{r Q1}
str(netflix)
```


Question 2 - List the variables in your dataset

```{r Q2}
names(netflix)
```


Question 3 - Print the top 15 rows of your dataset

```{r Q3}
head(netflix, 15)
```

Question 4 - Write a user defined function using any of the variables from the data set.

```{r Q4}
year_with_highest_frequency <- function(data) {
  year_counts <- table(data$release_year)
  year_with_highest <- names(year_counts)[which.max(year_counts)]
  return(year_with_highest)
}
year_highest_frequency <- year_with_highest_frequency(netflix)
```

Question 5 - Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.

```{r Q5}
shows_in_1990 <- subset(netflix, release_year == "1990")
print(shows_in_1990)
```

Question 6 - Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.

```{r Q6}
library(dplyr)
library(tidyr)
rating_counts <- netflix %>%
    group_by(release_year, rating) %>%
    summarise(count = n()) %>%
    ungroup()
rating_counts_wide <- rating_counts %>%
    pivot_wider(names_from = rating, values_from = count, values_fill = 0)
print(rating_counts_wide)
```

Question 7 - Remove missing values in your dataset.

```{r Q7}
netflix_clean <- na.omit(netflix)
```

Question 8 - Identify and remove duplicated data in your dataset

```{r Q8}
duplicated_rows <- duplicated(netflix)
netflix_unique <- netflix[!duplicated_rows, ]
```

Question 9 - Reorder multiple rows in descending order

```{r Q9}
netflix_ordered <- netflix[order(netflix$release_year, decreasing = TRUE), ]
```

Question 10 - Rename some of the column names in your dataset

```{r Q10}
names(netflix)[names(netflix) == "listed_in"] <- "Category"
```

Question 11 - Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)

```{r Q11}
netflix$release_year_double <- netflix$release_year * 2
```

Question 12 - Create a training set using random number generator engine

```{r Q12}
set.seed(123)
train_indices <- sample(nrow(netflix), 0.8 * nrow(netflix))
train_set <- netflix[train_indices, ]
```

Question 13 - Print the summary statistics of your dataset

```{r Q13}
summary(netflix)
```

Question 14 - Use any of the numerical variables from the dataset and perform the following statistical functions
Mean
Median
Mode
Range

```{r Q14}
# Mean
mean_release_year <- mean(netflix$release_year, na.rm = TRUE)

# Median
median_release_year <- median(netflix$release_year, na.rm = TRUE)

# Mode
mode_release_year <- Mode(netflix$release_year)

# Range
range_release_year <- range(netflix$release_year, na.rm = TRUE)
```

Questions 15 - Plot a scatter plot for any 2 variables in your dataset

```{r pressure, echo=FALSE}
netflix$duration_numeric <- as.numeric(gsub("[^0-9]", "", netflix$duration))

# Replaced 'Season' values with an assumed duration
season_duration <- 10 * 30  # Assumed duration for one season (10 episodes, 30 minutes each)

netflix$duration_numeric[grepl("Season", netflix$duration)] <- season_duration

plot(netflix$release_year, netflix$duration_numeric,
     xlab = "Release Year", ylab = "Duration (minutes)",
     main = "Scatter Plot of Release Year vs Duration", col = "blue")
```

Question 16 - Plot a bar plot for any 2 variables in your dataset

```{r pressure1, echo=FALSE}
barplot(table(netflix$rating),
              xlab = "Rating",
              ylab = "Count",
              main = "Bar Plot of Show Count by Rating", col = "red")
```

Question 17 - Find the correlation between any 2 variables by applying least square linear regression model

```{r Q17}
model <- lm(duration_numeric ~ release_year, data = netflix)
summary(model)
```